### 2012-11-13 doc/progress_plan/report.tex
Added some more references and basically finished lit review

It is proposed that Partridge should use the CoreSC schema for document storage
in order to provide a standard way to access and process the papers and thus
eliminate the task of dealing with multiple documents during its learning
phase. Using CoreSC also offers the advantage of making Partridge compatible
with the ART corpus. This is a set of physical chemistry and biochemistry
research papers that have been pre-processed and already annotated using CISP
concepts\cite{liakataART}. This would provide Partridge with a set of papers
that could be used as a training set for classification tasks and could be used
for information retrieval tests from early on in the project.

@@

@@

@@

There are also a number of search and indexing systems that specifically look
for scientific papers as opposed to web pages. One of the most publicised and
well known paper search system is Google Scholar
(\url{http://scholar.google.com}).  As can be seen in Figure
\ref{fig:scholar_basic}, This is an adaptation of Google's general search
engine (discussed above) to specifically index and search scientific papers.
Google also offers advanced query options specific to Scholar that allow
searching by author, year and for words that occur only in the document title
as shown in figure \ref{fig:scholar_advanced}. Whilst this does deal with the
problem of `information overload' and provides even more fine control over the
information returned from searches,  the user is still required to have a very
good idea of what they are looking for in terms of keywords and/or specific
authors. It is possible that a user would not know what they are looking for
until they've seen it. Even if the user has a set of keywords to search for,
they can only search the title of the paper or the content as a whole. This
means that users who want to find a particular phrase within a CoreSC part of
the paper (e.g. only look for this phrase in the `Result' section of the
paper) are unable to get results at their desired level of detail.

@@

Partridge will provide the option to filter papers by subject and it is hoped
that the system will also provide user-specific recommendations by profiling
them through their reading history. This will make it easier for users to find
relevant papers without knowing exactly which keywords they need to search for.
Partridge will also offer facilitate searching for keywords within a specific
CoreSC section by making use of Liakata et al's SAPIENTA project for
classifying each sentence of paper.

>>>>

It is proposed that Partridge uses the CoreSC schema for document storage
to provide a standard way to access and process the papers and thus
eliminate dealing with multiple documents during its learning phase. 
Using CoreSC also offers the advantage of making Partridge compatible
with the ART corpus. This is a set of physical chemistry and biochemistry
research papers that have been pre-processed and already annotated using CISP
concepts\cite{liakataART}. This would provide Partridge with a set of papers
that could be used as a training set for classification tasks and could be used
for information retrieval tests from early on in the project.

@@

After pre-processing by SAPIENTA is complete, Partridge will need to do some
classification work of its own to determine the area of study (i.e. Physics,
Chemistry, Biology), type of paper (Literature review, Case Study, Experiment)
and the polarity of the result (positive, negative, inconclusive). These tasks
involve implementing existing AI techniques and applying them specifically to
the task of text classification. To avoid the time consuming task of re-implementing these
methods, it was decided that a library should be used instead.

@@

There are several existing libraries to facilitate Natural Language Processing.
Many are written for Java \cite{mallet2002}\cite{cunningham2011text} and are
very complex or not well documented. The Natural Language Toolkit (NLTK) is a
simple and intuitive library written for Python. Bird(2009) states that NLTK
was designed ``to provide an intuitive framework along with substantial
building blocks, giving users a practical knowledge of NLP". The project is
relatively mature in comparison to the above named Java libraries. There is
also a free book that accompanies the project available at
\url{http://nltk.org/book/} which provides a huge amount of information on how
to implement many popular NLP techniques using the library. For this reason
NLTK was chosen as the primary accompanying library for the project.

@@

There are also a number of search and indexing systems that specifically look
for scientific papers as opposed to web pages. One of the most publicised and
well known paper search systems is Google Scholar
(\url{http://scholar.google.com}).  As can be seen in Figure
\ref{fig:scholar_basic}, This is an adaptation of Google's general search
engine (discussed above) to specifically index and search scientific papers.
Google also offers advanced query options specific to Scholar that allow
searching by author, year and for words that occur only in the document title
as shown in figure \ref{fig:scholar_advanced}. Whilst this does deal with the
problem of `information overload' and provides even more fine control over the
information returned from searches,  the user is still required to have a very
good idea of what they are looking for in terms of keywords and/or specific
authors. It is possible that a user would not know what they are looking for
until they've seen it. Even if the user has a set of keywords to search for,
they can only search the title of the paper or the content as a whole. This
means that users who want to find a particular phrase within a CoreSC part of
the paper (e.g. only look for this phrase in the `Result' section of the
paper) are unable to get results at their desired level of detail.

@@

Partridge will provide the option to filter papers by subject and it is hoped
that the system will also provide user-specific recommendations by profiling
them through their reading history. This will make it easier for users to find
relevant papers without knowing exactly which keywords they need to search for.
Partridge will also offer facilitate searching for keywords within a specific
CoreSC section by making use of Liakata et al's SAPIENTA project for
classifying each sentence of paper as it is added to the repository.
